Which Amazon Problem? Problem-constructions and Transnationalism in Brazilian

### 2023-02-17 Submission/Re-submission/draft/draft_resubmission_shorten.rmd
final version

---
title: "Which Amazon Problem? Problem-constructions and Transnationalism in Brazilian
  Presidential Discourse since 1985"
author:
- "Livio Silva-Muller"
- Henrique Sposito^[Both authors contributed equally to the article. Names are ordered
  alphabetically. Livio is a PhD Candidate in Sociology and affiliated to the Albert
  Hirschman Centre on Democracy. Henrique is a PhD Candidate in International Relations
  and Political Sciences and affiliated to the Centre for International Environmental
  Studies.]
date: "17 February 2023"
output:
  pdf_document: default
  latex_engine: xelatex
  fig_caption: yes
  html_document:
    df_print: paged
  word_document: default
fontsize: 12pt
mainfont: Times New Roman
header-includes:
- \usepackage{floatrow}
- \floatsetup[figure]{capposition=top}
- \usepackage{float}
- \floatplacement{figure}{H}
- \usepackage[T1]{fontenc}
- \usepackage[utf8]{inputenc}
- |
  \providecommand{\keywords}[1]{\textbf{Keywords:} #1}
  \providecommand{\wordcount}[1]{\textbf{Word Count:}#1}
always_allow_html: yes
bibliography: references.bib
csl: chicago.csl
abstract: The Amazon is a complex object of policy that comprises environmental, economic, social, and sovereignty concerns. Despite this complexity, governments are often portrayed as having a single understanding of the Amazon as a political problem. We investigate how the Amazon has been constructed as a problem in Brazilian presidential speeches. To do so, we develop a framework that accounts for how important actors in transnational politics, as presidents, construct policy objects as particular problems depending on where and when they participate in politics. Using supervised machine learning, we classify statements about the Amazon in 6240 presidential speeches since 1985. We find that Brazilian presidents often construct the Amazon as an environmental problem when speaking far away from the region, whereas they usually construct it as problems of economic integration or social development when in the Amazon. Furthermore, presidents increasingly construct the Amazon as multiple problems rather than a dichotomy between economic or environmental problems.
---

```{=latex}
\keywords{ discourse analysis, presidential speeches, transnational governance, environmental policy, Brazilian Amazon, supervised learning}
```
```{=latex}
\wordcount{ 7900 (including text, endnotes, footnotes and references)}
```
```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(dplyr)
library(tidyr)
library(scales)
library(RColorBrewer)
library(stargazer)
library(kableExtra)
library(tibble)
library(ggplot2)
library(plm)
library(timetk)
library(lubridate)
Sys.setlocale("LC_ALL", "C")
options(stringsAsFactors = FALSE, scipen = 999)
```

@@

We use fixed-effect logistic regression models to predict the probability of a speech mentioning the Amazon and each of the four problem-constructions. The fixed-effects models are indexed by the president, since each president might have individual-specific characteristics that can influence outcomes. Both presidents' political ideology and setting preferences[^2] could affect problem-construction. Fixed-effects models help to control for these possible individual-specific issues and other unit-unvarying characteristics [@allison2009].

[^2]: Figure 5 (in appendix) confirms presidents have a similar share of speeches by setting, weakening the possibility of presidents picking settings according to their agendas.

@@

We interpret the increased balance in pure-types and the general increase in mixed-types Amazonian problem-construction as evidence that presidents increasingly find ways to reconcile the dichotomy between economic and the environmental ways of representing the Amazon as a problem. This suggests that the Amazon is becoming increasingly recognized as an intricate policy object in transnational politics.

>>>>

---
title: "Which Amazon Problem? Problem-constructions and Transnationalism in Brazilian
  Presidential Discourse since 1985"
author:
- "Livio Silva-Muller"
- Henrique Sposito^[Both authors contributed equally to the article. Names are ordered
  alphabetically. Livio is a PhD Candidate in Sociology and affiliated to the Albert
  Hirschman Centre on Democracy. Henrique is a PhD Candidate in International Relations
  and Political Sciences and affiliated to the Centre for International Environmental
  Studies.]
date: "17 February 2023"
output:
  pdf_document: default
  latex_engine: xelatex
  fig_caption: yes
  html_document:
    df_print: paged
  word_document: default
fontsize: 12pt
mainfont: Times New Roman
header-includes:
- \usepackage{floatrow}
- \floatsetup[figure]{capposition=top}
- \usepackage{float}
- \floatplacement{figure}{H}
- \usepackage[T1]{fontenc}
- \usepackage[utf8]{inputenc}
- |
  \providecommand{\keywords}[1]{\textbf{Keywords:} #1}
  \providecommand{\wordcount}[1]{\textbf{Word Count:}#1}
always_allow_html: yes
bibliography: references.bib
csl: chicago.csl
abstract: The Amazon is a complex object of policy that comprises environmental, economic, social, and sovereignty concerns. Despite this complexity, governments are often portrayed as having a single understanding of the region as a political problem. In this article, we investigate how the Amazon has been constructed as a problem in Brazilian presidential speeches since 1985.To do so, we develop a framework that accounts for how important transnational actors, as presidents, construct policy objects as particular problems depending on where and when they participate in politics. We find that presidents often construct the Amazon as an environmental problem when speaking far away from the region, whereas they usually construct it as problems of economic integration or social development when in the Amazon. Furthermore, presidents are increasingly more likely to mix problem-constructions and construct the Amazon as a complex and multifaceted object of policy.
---

```{=latex}
\keywords{ discourse analysis, presidential speeches, transnational governance, environmental policy, Brazilian Amazon, supervised learning}
```
```{=latex}
\wordcount{ 7969 (including abstract, text, endnotes, and references)}
```
```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(dplyr)
library(tidyr)
library(scales)
library(RColorBrewer)
library(stargazer)
library(kableExtra)
library(tibble)
library(ggplot2)
library(plm)
library(timetk)
library(lubridate)
Sys.setlocale("LC_ALL", "C")
options(stringsAsFactors = FALSE, scipen = 999)
```

@@

We use fixed-effect logistic regression models to predict the probability of a speech mentioning the Amazon and each of the four problem-constructions. The fixed-effects models are indexed by the president, since each president might have individual-specific characteristics that can influence outcomes. Both presidents' political ideology and setting preferences could affect problem-construction[^2]. Fixed-effects models help to control for these possible individual-specific issues and other unit-unvarying characteristics [@allison2009].

[^2]: We conducted more direct tests of these effects and added results in the appendix. While table 3 shows the limited effect of presidents' party ideology; figure 5 confirms presidents have a similar share of speeches by setting, weakening the possibility of presidents picking settings according to their agendas.

@@
